\input{preamble}
\begin{document}

\section{Goals of This Semester}
In this semester there has been set some goals, which are meant to be reached during the semester These goals are: 

\textbf{Knowledge:} \newline
	The student will after completed project-module be able to:
	\begin{itemize}
			\item Understand and account for syntax and behavior of language constructions in a concrete programming language, and how they work.
	\end{itemize}

\textbf{Skills:} \newline
	The student must after a completed project-module be able to:
	\begin{itemize}
		\item Implement a larger program. This includes utilizing and understanding concepts, structures and facilities in the programming language, and on this basis construct a well-structured program
		\item Complete a test of the program which, in fair extend, ensures that the developed program corresponds with the problem statement. 
	\end{itemize}

\textbf{Competences:} \newline
	After completion of the project-module, the student must be able to:
	\begin{itemize}
		\item Delimit a problem and in this issue articulate and defend a problem, which can be solved by programming, as a main-part of the method to 		solve the problem.	
		\item Develop a model, which can be applied in connection with the solution of the selected problem. 
		\item Complete the work to a runable and demonstrable program, and hereby show skills at delimiting. 
		\item Describe how the program solves a formulated problem within the context of the problem statement. 
		\item Include relevant use-related an social aspect of solutions within computer science and software technology.
		\item Describe, reflect and analyze the gained experiences with working with a problem based project in a group.
	\end{itemize}

\textbf{What has been done to reach these goals?} \newline
All members in the group have followed this semester's three courses: Object Oriented Programming, Computer Architecture, and Discrete Mathematics. We have used techniques and skills gained in these courses in our project.

\textbf{Did we reach these goals?} \newline
	The knowledge goal has been reached. This is reflected in our program, which is a working suitcase packing program. The skills goal has also been reached. We have implemented a larger program, and constructed both user- and unit tests on this program. We are now able to find a problem, delimit it, and solve it using programming as the main-solution to the problem. We have developed models for the program, and in the conclusion in the report, it is described how the problem solves the problem within the problem statement. We included use-related aspects of the solution by creating a program which solves the problem of packing a suitcase properly. The whole project is the result of the reflection and analyzes we have made by working with a problem based project. Therefore the competences goal has also been reached. 




\end{document}