\section{Trip types}
There are many different reasons to travel.
One could be a business trip for a company or it could be to go on a vacation.

For the vacation there is also different reasons to travel:

\textbf{Around the world}
This form of travel is to see the world one country at a time and to clear ones mind before doing something like taking a long education or start working.

\textbf{Adventure trip}
This is a trip that have the purpose to give greats experiences that one normally do not get on a trip.

Active and adrenaline and/or Diving, surfing, (Courses) sailing:
this trip is for people that want some action on there trip instead of a relaxing trip where. The focus on those trip is sports, see the nature...
http://www.packinglistplace.com/divinglist

ESSENTIAL DIVING GEAR

Dive Bag - Mask - Fins - Snorkel - Wet Suit (as necessary -- pants, vest, jacket, hood, farmer john) - Spandex-type shorts (great for under wet suit) - Dive Boots/Shoes - Gloves - BCD - Regulator (is the annual inspection current?) - Submersible Pressure Gauge (SPG) - Depth Gauge - Compass - Dive Knife - Dive Watch - Dive Computer - Weight Belt - Tank (is it filled?)

ACCESSORIES

Dive Lights(s) (Does it work? Has fresh batteries?) - Dive Flag - Safety Sausage - Whistle - Camera, Batteries and Memory Card (or film) - Buddy - Line - Slate & Pencil - Lift Bag - Save-A-Dive Kit - Tools (as necessary) - Extra Weights (as necessary)


Safari and nature:
this trip to people that want to see wild life or the nature that they do not see every day. An example could be a trip to Africa to the savannah.

Volunteer work:
this is for people that want to help on there trip. They can choose between help people that need help. work with the nature and the environment or help with taking care of wild animal
http://www.seeturtles.org/687/volunteer-project-packing-list.html

First aid kit - Lightweight dark colored clothing, preferably long-sleeved and quick drying - Sunscreen - Mosquito repellant - Headlamp (preferably one with a red setting) or flashlight and batteries - Rain jacket or poncho - Rain boots or lightweight shoes - Refillable water bottle - Alarm clock - Teva, Crocs, or Keen-type sandals - Swimsuit

City and Festival:
those trips are for people that want to see a major city in another country or to experience a certain festival that is hold somewhere 

Working Holiday:
here one can travel and earn money then on a trip by working. Here you can the culture and people from a other country. 

Road trip:
on this trip oneself is en control when and where to stop on the trip. there is still some things that need to be settled on the trip, like then and where to start and end the trip, the period of time the trip are. on road trip one often loan a car. But else the trip is op to oneself, what to eat, self made food or eating on restaurants, to sleep in the car or to sleep in a motel/hotel.