\input{preamble}
\begin{document}
\section{Other passport photo programs}
In this section there will be taken a closer look on what other programs exist that could help a user make a pass photo. In the following there will be a short description of the program and at the end a summary of what features the program of this project will have and what it will not have based on what the other programs offers.

\subsection{CNET Editors: CamToPrint}
This program helps with making the passport photo in the way that the user wants it. First you start by choosing a picture you want to make into a passport photo and the programs help center and crop it to the right size. Then the program offers some tools to help with adjusting brightness and contrast. Under the menu you can see the passport photo requirements for The United States of America or United Kingdom. When you are finished with the photo you can choose to print it directly from the program or save the photo as a file for later use.
But this program offer more functions than just tools for making passport photo program. It offer some others photo tools, like utilities for making photo albums, calendars, greeting cards, and collages.\citep{pass_soft_c_net}
\newline


\subsection{OnTheGoSoft}
This program help with making the passport photo with the functions to select passport photo size, rotate and cut the photo. The size formats that you can select from goes for the US, Canadian, standard or custom passport photo size.
Besides this the program also helps with the printing of the photo so you get a lot of photos on a single page.\citep{on_the_go}
\newline

\subsection{ePassportPhoto.com}
This is not a program but rather a website that helps the customer with the editing of the photo by allowing access to some tools that the user can use to scale the photo into the right format and it gives a good explanation on how to edit the photo. After editing the photo you can download the edited photo and print it from your own computer.
But this site offers more help if you are willing to pay a fee of 9,99 dollars. For this price you get a passport photo expert to inspect the photo and check that all things required in the photo is in order. If you don't get the photo approved you will get a refund.\citep{ePass}
\newline

\subsection{Passport Photo Studio}
This program helps by cropping the photo to the right size but you have to help it finding the head with a circle where the head needs to be in the center of the circle. After this you have to choose what passport photo rules the photo needs to follow either USA or United Kingdom (EU).\citep{PPS}
\newline
\newpage
\subsection{ePhotozine}
This is not a program but a set of guidelines on how to make a passport photo in a photo editing program, like Adobe Photo-shop. It gives a list over what the rules requires of a passport photo.\citep{ePz}
\newline

\subsection{Summary}
Here is a summary of what the program of this project will have and will not have based on what the other programs listed above have.
\newline\newline
\textbf{What the program will have}
\newline
The program is suppose to be a help to the user so they can easily produce a pass photo image that will follow the requirement for pass photos. The user will mark the area of the head, the program will then scale it to fit the size of a pass photo and check if the image have a high enough PPI (Pixel per inch). The program will then follow up with safety questions to make sure the user have remembered all the requirements for the photo.
\newline

\textbf{What the program will not have}
\newline
Given the nature of the program it will not include the feature to make albums, calenders or greeting cards because they have no relation to pass photos. And because of the limited visual functions of C programming, the program will not have an interface as such, only lines which to write on. Furthermore the program is intended to substitute for an image expert so it will help the user check whether or not the photo follows the requirements. And for the same reason the program will not print the photo, though it would be nice to have.
\newline


\textbf{Nice to have}
\newline
The program does not take into account that an image might be turned to one side. So a "nice to have" feature would be a rotate function that will solve said problem. The program of this project is based on European requirements for photos but some countries have different requirements so to further increase usability a plug-in or a built-in feature to choose from different countries would be preferable.

\end{document}