\section{Problem}
In the modern society, families or groups of friends tend to go on vacation to other countries to relax and enjoy their vacation or explore the world \citep{danskecharter}.

When going on a vacation or a business trip packing a suitcase is normally needed. You need all you personal items and clothes with you. The length of the stay, the purpose of the trip, and the number of people travelling together effects the weight and size of the luggage. This can be a problem due to the different rules or limits to your luggage when using different means of transformation.\\

The time spend away affects how much clothes the traveller will need to bring and/or if the traveller will need to wash the cloth while away. A longer stay means of cause that the traveller will need more clothes. This affects the size and weight of the luggage because you will need more or fewer items with you on different trips.\\
 
The amount of items to bring also depends on what kind of trip it is and the purpose of the trip. For example if the purpose of the trip is a sport competition, you might need to bring some equipment, you would not normally bring on a holiday trip or other kind of trips. If it is a short business trip all you might need could be a briefcase with your papers and a suit to wear.\\

The amount of luggage depends on the amount of people on the trip, because everyone needs their own personal items, and their own clothes. This can be a problem if the persons have a lot of shared items that has to be spread in different suitcases and need to be found afterwards and it might also effect the total weight of the luggage.\\

It can be frustrating, when travelling with many and/or heavy suitcases, if you need to carry the luggage far. It can also be hard to manoeuvre if where you are suppose to walk is a small space or a narrow passage or if simply filled with a lot of people constantly blocking your way.\\
 
There can also be a problem with too large or heavy suitcases if you are travelling by plane since this can result in a fee. The size of the fee varies from airline to airline and can be found on the airlines website e.g.  \citep{altombag}. One of the reasons that this fee has been introduced is so the airlines bag-handlers do not risk getting injuries by carrying too many, heavy suitcases.\\ 
To avoid this fee it can be an advantage to pack the suitcases properly and limit the choice of items to bring so the total weight does not exceed the allowed weight.\\

\subsection*{Packing}

Because of the weight and size restrictions at the airports it can sometimes be difficult to get all the items you want to bring into a suitcase that is small enough and not exceed the allowed weight. It can sometimes be necessary to acquire more suitcases for the trip or leaving some of the items you wanted to bring. 
Bringing more luggage means you have to pay more to get the extra luggage with you on the plane. A way you might be able to avoid buying and paying for extra suitcases is to pack the suitcases more than the suitcases are meant to contain. This mean that the suitcases packed more compact. This on the other hand increases the bags weight \citep{altombag}. This should be thought through because too much weight can be unhealthy to carry around.

The increased weight means the bags might exceed the limit for weight and therefore trigger a fee for overweight luggage.
It seems people often pack their luggage more compact instead of taking extra bags with them on vacation. Generally people take a lot with them on vacation and they might not have packed their luggage the most effective way \citep{airstat}.

\begin{table}[H]
\begin{tabular}{| l | r | r | r | r |}
\hline
Airline &  First quarter & Second quarter & Third quarter & Summery for 2011 \\ \hline
Delta & 197,971 & 226,291 & 232,508 & 656,770 \\ \hline
American & 137,210 & 156,114 & 152,750 & 446,074 \\ \hline
US Airways & 120,925 & 134,752 & 128,761 & 384,439 \\ \hline
Continental & 76,304 & 91,332 & 94,301 & 261,937\\ \hline
United & 66,245 & 71,111 & 74,758 & 212,114 \\ \hline
\end{tabular}
\caption{This table contains the top 5 of the companies that have collected the most fees in 2011. The numbers are from \citep{airstat} and the fourth quarter is not released yet, therefore missing}
\label{tab:airlinefees}
\end{table}

An American website for statistics, \citep{airstat}, shows the amount of fees given regarding luggage that have been registered at the U.S. airlines. Table \ref{tab:airlinefees} is a segment of the statistic table found at \citep{airstat}. Through this it is possible to see that there are people that exceed the set of limits given by the airline. A note regarding this source is that the size of the fee is a combination of the different rules and related fees. Therefore the statistics do not give an accurate image of the problem with weight limit, but a more general image of the problems with luggage exceeding the given limits.

The problem with packing luggage is mostly the same if it is by train, car, or flights. But flights is the one transport where it plays the biggest role for the traveller because it has economical consequences. With train and car it is more or less up to the traveller how heavy the luggage is allowed to be. There are restrictions to how big the bags are allowed to be in the train. For train the limits are 100 x 60 x 30 cm \citep{rulestrain}.

When going on vacation, and using the car as transportation, the size of the car sets the limit in size of the luggage, since you cannot just pay to get more luggage with you than fits into your car. The weight might also have a influence on the amount of luggage there can be in the car. Because the car might not be able to drive well if the certain car is over the excess weight, since there are cars that can lift more than others. % When packing a car it is important to place the heaviest of the luggage just behind the back seats and evenly spread to the sides. This is to prevent the luggage from gathering momentum during an emergency brake and maybe go through the back seats. Furthermore it is to prevent over steering and thereby evade potential traffic accidents\citep{Farlig_bagage}.

There can be many good experiences and memories on a vacations. The memories tend to be bound to photos, items and souvenirs and thereby makes it easier to remember. Souvenirs can have a certain value and can be used to fill the home with memories about the past experiences.
With this in the mind, it is important to make room for possible souvenirs or other things that simply had to be bought while away.

These souvenirs can be a problem to bring home. As earlier mentioned the weight and size of the luggage is a problem before the departure, therefore it will normally also be a problem on the trip home.
This means that if a family packs just to the limits and then buy things and souvenirs on their vacation they will get into trouble when packing the luggage for the trip home.

So the general problem is packing the luggage in the most effective way and spreading the weight in the available suitcases, without violating the different rules or limits to size and weight. It can also be a problem to pack the suitcases to the trip home due to the bought souvenirs or other items.

The reason to the problem could be that people find it difficult to pack the luggage for a trip and therefore pack more than they actually need on the trip.

The consequences of luggage exceeding the weight limits at the airlines are that the traveller will have to pay a fee for the extra weight.
Train passenger that exceed the size limits might not be allowed to have their luggage with them if the dimensions of the suitcases are to big.
There is not a program on the marked that specifically helps packing luggage for a trip, but there exits at least one program that can pack a container\citep{solvingmaze}. This method of packing a container can be compared to packing luggage. A other solution is a smart-phone application that help with packing a suitcases by making a check-list over what to have with you on the trip \citep{packingpro}.