\section{Method}
This project structure will be based on Aalborg PBL (problem based learning). The Aalborg PBL is a method whereby the learning process lies in the work with a problem and try to develop a solution for the given problem.
The Aalborg PBL method also trains the students ability to work together in a project group and give them tools to handle the processes that goes with working in a group.

The first stage of the project is the problem analysis, which purpose is to find and document that there is a problem to begin with. From the problem analysis a thesis statement is formed and is used to produce a list of product requirements.
The requirements are then use to design and develop a product that should solve the problem stated in the thesis statement.
The program are then tested on the target group of the problem. The testing leads to a conclusion of the project. This is the main focus of the project, when using the Aalborg PBL.
This project form is used because it finds and document a problem and then through the work with the problem gives an estimated solution to the problem.\\

To document the problem, a lot of information is needed. The information is found through different sources such as; books, article, websites, etc. When using information found through the internet or other sources it is important to evaluate the used sources.
This is done to filter out unreliable sources and thereby achieve a better and more trustworthy project.
This process of evaluation is also known as source criticism and are general used when using others materials as documentation. Therefore it is also a relevant method to use when using sources in the project work.\\
