\section{Choice of Survey Method}
To test the person and see how a customer would react to the program. Tests were made where the test persons tried the program and they got interviewed afterwards. For the analysis and further work regarding the test results, a qualitative method has been chosen.

For the interview there has been made a questionnaire (see appendix ?), that will be used as a guideline in the interview to get the right information from the test person. The qualitative method is the best suited method for the project, because it gives a more specific picture of how the test person finds the program, and what problems the test person might come across during the test. It is also a good method to get suggestions to improvements from the user since it normally is easier to explain an idea while talking rather than writing. The problem with the interview is that the time it takes to analyse is longer than a questionnaire, where you quickly can analyse a lot of data. The questions at the interview need to be well thought and precise to get the right information from the test person, as they would also need to be on a questionnaire. From the test improvements should be made to the program. 
It is important when making a questionnaire that it is structured correctly and that the questions are precisely formulated so the test person cannot misunderstand the meaning of the question. It is important because poorly formulated questions might lead to misunderstanding the meaning of the question which can lead to wrong or useless answers. And in such case is a questionnaire just a waste of time.

So there will be made an interview based on a questionnaire after the test person has tested the program with focus on what can be improved on the program.

\section{The First Round of Tests of the Program}
Two tests of the program have been made on two different test persons in the first round of tests. The main idea was to see if the program had any bugs and to get some suggestions to what could be improved and if anything was missing. The test persons were first given some instructions on what they were supposed to do in the test and were afterwards asked to read the instructions in the program. The test persons were to load two lists in the program and then add some missing items after having measured the item's weight and dimensions. Then afterwards they were asked to pack two suitcases. When the test persons were done packing an interview was made. Two group members were present at the testing. One was sitting documenting everything and afterwards interviewing the test person, while the other sat behind the test person to see what mistakes the test person made.

After the first test some labels in the program was changed to help the understanding of the use of the program. The instructions in the program were also changed to better describe more of the program. The first test person did not have problems at all in packing the suitcases but stated that he/she did not find the program useful. He/she suggested adding a function making the program able to take into account if an item is bendable.

The second test got interrupted because of some problems with loading one of the lists which caused a breakdown of the program. The test was retaken another day after the problem was fixed. Before the 2nd test we made some changes in the instructions, saving functions, bottom of suitcase, added some new buttons on the forms; manage suitcase, manage items, add item, and add suitcase. After we made those changes we began test 2.

The second attempt on the second test was made a short time after the first attempt. This time there was no technical problems with the program, and the test was made without more serious problems. After the test the instructions was changed again to better describe some features in the program and also describe how to rotate and drag the 3D model in the 3D-viewer. Another thing that was changed was that you now have to write the weight limit in kg instead of gram. The mistake with the program asking if you want to save the lists after you have saved them by using the button was also fixed after the test. The "Reset"-button  was removed from the main window. The list in the 3D-viewer now sort the items so the ones on the bottom is in the top of the list now. The last thing that was changed was that an image of a suitcase was added in the "Manage Suitcases"-window and a picture of several items was added to the "Manage Items"-window.

\section{The Second Round of Tests of the Program}
In the second round of tests we tested two test persons. Some small improvements to the test method was made in this round of tests. The instructions about what would happen in the test was written down instead of just told so the test person would not forget the instructions, and and the instructions was improved so they were easier to understand.

The second round of tests was made a week after the second test. The test went without any technological problems and was an success. After the two tests the following was changed. Since both test persons complained about the time it would take to put in all the info needed in the program, a drop down menu of some standard items has been added in the "Add item"-window in the "Manage items"-window. A better description of what is the bottom in the suitcase has been added in the 3D-viewer. The little box showing the (0,0,0)-coordinate has been described in the 3D-viewer too. The problem about a lot of items being packed upright was been solved and the algorithm has been optimized. A better description on how to add more of the same thing has been added to the instructions. If you are managing a already saved list and click the "Save list to Computer"-button the program will now ask if you want to overwrite your saved list. In the 3D-viewer the unit for the suitcase(s) weight has been added. 

\section{Conclusion on the Tests}
The test went well and the group got some good feedback that lead to some great improvements to the program and the bugs in the program was fixed. Most of the test persons found the program useful if they had to pack a lot to a vacation. Testing more than once proved a very good idea since all the test persons had good suggestions to improvements and found minor bugs that quickly was fixed. If anything should be better next time the group should test it was to be sure to write down the instructions to the test person and be sure everything is ready for the test person. But all in all some very successful tests.



