This chapter is about the group's teamwork and how the work is administered.
\section{Division of roles}
The group members have different roles and each role has different responsibilities. There are the group coordinator, moderator, reporter, postman, writers of the worksheet and Conflict Emergency Team (CET).

The roles are:
\begin{itemize}
\item The group coordinator is in charge of the time schedule, keeps the general overview and keeps the contact to everyone outside of the group.
\item The moderator makes sure the agenda at the meeting is being followed and that the meeting is being taken serious.
\item The reporter writes the summery of every meeting both with the supervisor and other outside the group and at the groups own meetings if needed.
\item The postman is in charge of getting the post.
\item The writers of the worksheet are in charge of making the worksheet and having it ready before deadline.
\item CET is in charge of solving any conflicts that might arise in the group.
\end{itemize}

\section{Administration}
The group coordinator is in charge of coordinating the work in the group and updating the time schedule. It is also the group coordinator's responsibility to make the deadlines and that the group is following these deadlines on the time schedule.
\section{Decision making}
Every important decision is made with at least 5 group members present and any missing members will be notified about the decision. The group contract and our key contract were made with all the group members present. (The group contract can be found after this chapter).
\section{The meeting culture}
The meeting time is from 9.10-16.15 each workday if the group has no classes. In the case of a class in the morning is the meeting time 8.15-16.15.
A member of the group are allowed to leave at 14.00 if the group have no classes in the afternoon but have to work the remaining 2 hours and 15 minutes at home.
\section{Responsibility for own learning/mutual responsibility for learning}
Each group member has responsibility for his/her own studying at home and at class. But the group also has mutual responsibility for the group's studying while there is group work. 
Knowledge sharing is also important and the group uses SVN to share all work so it is available at all time to everyone in the group.