\section{Division of Rules}
From last semester's group work and the PV course last semester did we learn that is was a good idea to have certain roles divided among the group members. When assigned a role one's role does not change throughout the semester. The group allowed every member to decide for themselves if they wanted a specific role but all roles were divided among the group members so it were not only a few who had special roles in the group.

Having solid roles is a good idea because they make sure that there are an overview of the project and that the needed things will be done - like updating the time schedule and write down what happens at the meetings.
There were some roles that also were used on last semester that we found very important. The roles were project coordinator, agenda manager, reporter and a conflict solving team. A change from last semester is that the coordinator now also has the job to keep contact with the supervisor.
The group coordinator is the most important role in the group since he/she has the responsibility to keep the big overview of the project, update the time schedule, and keep contact to the supervisor. 
The agenda manager and reporter has the responsibility to control and write a summery of the meetings. These documents were then saved for later use. Conflict Emergency Team (CET) is the group's conflict solving team if any conflict should happen in the group. The CET consists of 3 members so if two of the members are in a conflict then the last one will be able to try and solve it.

We would like to keep these roles for the next semester since it works very well. We think it is important to have these roles and that only one group member have a role for the whole semester if able since it is not always easy to take over a role you are not used to fill.
