\input{preamble}
\begin{document}
\chapter{Group Contract}
\label{chap:groupcontract}
\textbf{B130 - 3/2/12}
\section*{Rules}
\renewcommand{\labelenumi}{§ \arabic{enumi}}
\renewcommand{\labelenumii}{\alph{enumii}}
\begin{enumerate}
\item If anyone breaks rule 2-9 the rulebreaking person has to buy cake/sandwich/pizza or the like to the other group members.
\item Keep appointments - also meeting time. 
	\begin{enumerate}
	\item You need to notice the other group members if you are unable to come or are late.
	\end{enumerate}
\item A normal workday is from 9:10-16:15, unless there is a class in the morning - Then the meeting time is when the class starts.
\item Everybody need to be ready to work at 9:10.
\item Lunch is from 12.00-12.30.
\item Be professionelly dedicated about work, the classes and the solving of group work.
\item All appointments about deadlines on parts of the project must be kept.
\item For all work related documents or other things \LaTeX~and SVN is used.
\item If a groupmember does not participate in the groupwork, or are doing something unserious, the other groupmembers can shout "Chicken" at the person. If a person gets 3 "Chickens", they must be punished according to §1.
\item There are high ambitions about the project.
\item When the group is making important decisions a minimum of 5 group members have to be present 
	\begin{enumerate}
	\item All decisions will be put in the folder "Beslutninger" - Group members not present are notified by sms.
	\end{enumerate}
\item 2 group members work on the worksheet.  If the work is not satisfying 2 new group members will be assigned the work.
\item There will be a morning-meeting from 9:10-9:20 every work day, where we do not have classes. In that case the meeting will be right after the class.
\item If the workload is to much for a group member the rest of the group need to be notified as fast as possible.
\item The group coordinator has the responsibility that this problem is solved. 
\item The group coordinator has the responsibility that the time schedule is followed.
\item It is a common responsibility in the group that all the group members are serious about the work.
\item Friday meeting is every Friday morning unless the group have to go to class - in this case the meeting is Thursday morning. 		\begin{enumerate}
	\item On this meeting the work of the day and and the weeks work will be discussed 
\item It will be checked if the time schedule is being follow 
\item Common thread (Where do we want to go? What happens now?) 
\item The worksheet are to be send before 12.00 Friday. The worksheet is made just after the meeting. The structure of the worksheet is discussed on the meeting. The worksheets is send to the contact person.
\item If any group member knowingly, repeatly breakes the rules, CET is responsable that it is dicussed on a group meeting.  
\end{enumerate}
\end{enumerate}

Also see "Nøglesamarbejdsaftalen" - (The contract about keys the the group room)

\section*{Group roles}

Coordinator: Christian (If not present Mette)
\newline
\newline
Moderator: Dag (If not present Aleksander)
\newline
\newline
Reporter: Mette (If not present Dag)
\newline
\newline
Contactperson: Christian
\newline
\newline
Postman: Rasmus
\newline
\newline
Writers of the worksheet: Aleksander and Niels
\newline
\newline
CET - Conflict Emergency Team: Mette or Kasper or Christian (Only one person needs to solve the conflict but is she/he is in the conflict another member of CET has to solve the conflict)

\end{document}