\chapter{Discussion and Putting Things into Perspective}
In this chapter we will discuss and perspective over this project and the work regarding it.
The planned time we work at the project was from 9:20 to 16:15 everyday if there was not planned any lectures. By doing this there was a high productivity in the group, but still there was time fun things. Also to help better work there where the option to work at home from 14:00, but this option was remove Temporary, 
%around the middle of the project because we where getting behind the project schedule,
and when together we usually stay at the same group room with meant that there was a high productivity in the group.
One of the good factors for a group is that social and friendly with each others because it enhances and improved the group spirit.
This can be useful for work in the future that you can work with other people and be part of a group.

we had a nearly had a meeting with the supervisor every week to make sure that we where on the right track with the project all the time, there was a single time when a supervisor meeting was pointless because the week before the only think that had been made on was the program. The overview of our project was easy to keep since the structure of the report was well organized. The schedule was well made with made it easy keep track of the project process. In this project there was a few roles in the group, the roles that were the was the one that we think where necessary to make sure the group work optimally together. This time there was only made a summary for the meetings with the supervisor and not for every day since it was not use that much en the previous project. 

Compared to our P1 project, we have to worked somewhat harder, with the result where a better report and a good product. Our working progress has been nearly the same, but since we get behind the schedule for the project. We have to work a little more harder in the next project. but the method for project work and makes the process easier to comprehend whit make it good for future project.