\section{Problem Statement}
\label{sec:thesis}
In this section a problem statement will be formulated which will be used to develop a method to the problem of this project and to get a more precise problem to work with. The method is used to try and solve the problem stated in the thesis statement.\\
The problem analyses shows that there are two general types of programs on the market. One type is a form of a packing list that tells the user what they might want to pack, the other type of program is a packing program which packs containers for the user and calculates the shipping cost to a designated location. These two types of programs only fulfill parts of the criteria this project have put forward. With this in mind a thesis statement have been formulated to help shape the solution for this projects problem.

\begin{itemize}
\item How can a program be developed which helps the customer through the progress of packing one or more suitcases the most effective way by size and weight?
\end{itemize}

The meaning of this thesis statement is to research and develop a program that in some way could handle the problem, but the consumer also plays a role in the problem.
Therefore the consumer must also be taken into account when it is being developed. The reason for this is to make the program as user friendly as possible.

\subsection*{Sub Statements}
The sub statements have been made to help find a solution to the thesis statement. These sub statements describe some of the steps that need to be made in order to find the solution for the thesis statement.

\begin{itemize}
\item \textbf{How can it be checked that the weight in the suitcases are evenly distributed and it does not exceed the allowed weight or the volume in the bag?}\\

The program will need to handle and solve calculations with weight and volume. Through these algorithms the program should find the must most effective solution for the given data. It will also have to check that the solutions weight does not exceed the given limits or the volume of the luggage.

\item \textbf{Which functions are needed to get the program to compute the most effective way to fit the items into the suitcases?}\newline

Some functions are needed for the program to find the most effective solution. The functions will use an algorithm for optimising and thereby the program will fulfil its purpose.

\item \textbf{How should the program communicate with the user and inform where the items are placed, and tell how much space is left?}\\

The program will have to be developed and tested so the customer can use the program to its full extent. Therefore it is important not to use advanced technical language or unexplained abbreviations.

\item \textbf{How can a program be developed so it takes the length of the journey  into account, and enable the user to update the program on the go?}\\

The program should also be developed so it is possible for the user to update the programs database while on vacation thereby get a packing order for the new content of the bags.
\end{itemize}

From this thesis statement there will be developed a list of requirements for the program, which it will need, to solve the given problem and be user friendly. The system requirements can be seen on section \ref{sec:Spec}
