\section{Specification Requirements}
\label{sec:Spec}
The program has some features, which are essential for the program to work, these are catalogued as "targeted features". The other features, the program does not necessarily need to work, is catalogued as "Nice to have" features.
\newline

\subsection{Targeted Features}
These are the features that the program will have. 

\textbf{Guide the user}:
The program will have a little readme file, or other form of guide, that will tell the customer how to use the program..
\newline

\textbf{Distribute weight}:
The program must be able to distribute weight of items evenly in each individual suitcase and if needed spread out in multiple suitcases.
\newline

\textbf{Distribute space}:
The program also needs to distribute the items by space. The whole idea of the program, is that it should be able to pack the suitcase, and be able to tell if there is enough space for eventual souvenirs. Lastly it should inform the user how much space, if any, is left.
\newline

\textbf{Account for the trips length}:
If a long trip is planned, the program must be able to account for more souvenirs.
\newline

\textbf{On the road}:
The program will be able to tell you, while you are on the trip, if there is enough space for a souvenirs, if you input the dimensions and weight of that item. 
\newline

\textbf{Baggage rules}:
The program will need to know basic baggage rules. For example the luggage must not weigh too much, and it must be below certain dimensions. 
\newline

\textbf{Where in the suitcase}:
When the user asks the program if an item will fit in the suitcase, the program will show exactly where in the suitcase the item will fit.
\newline

\textbf{Solid/liquid/bendable shapes}:
The program will also take in account that items might be bendable, and therefore fit in other ways than solid items. For instance a T-shirt can be folded in many ways and thus can be considered a liquid form as it can fit almost everywhere.
\newline

\textbf{Packing list}:
To make it easier for the user to know what will be packed an editable lists will be included depending on the type of trip.
\newline


\subsection{Optional Features}

\textbf{Type of trip}
Depending on the nature of the trip different packing lists will be necessary because each trip might require different items.
\newline

\textbf{Number of people}
Usually a trip is done with more then one person, so more suitcases might be available to distribute items between.
\newline