\chapter{Teamwork}
This chapter is about the groups teamwork and how the work is administrated.
\section{Division of roles}
The group has different roles and each role have different responsibilities. There are the group coordinator, moderator, reporter, postman, writers of the worksheet and CET (conflict emergency team).
The group coordinator is in charge of the time schedule, keeps the general overview and keeps the contact to everyone outside the group. 
The moderator makes sure the agenda at the meeting are being followed and that the meeting is being taken serious.
The reporter writes the summery at every meeting both with the supervisor and other outside the group and at the groups own meetings if needed.
The postman is in charge of getting the post.
The writers of the worksheet are in charge of making the worksheet and having it ready before deadline.
CET is in charge of solving any conflicts that might arise in the group.
\section{Administration}
The group coordinator is charge of coordinating the work in the group and updating the time schedule. It is also the group coordinators responsibility to keep track of if the group are following the time schedule or are late.
\section{Dicision making}
Every important decision is made with at least 5 group members present and any missing members will be notified about the decision. The group contract and “nøglesamarbejdsaftale” were made with all the group members present. (The group contract can be found after this chapter).
\section{The meeting culture}
The meeting time is from 9.10-16.15 each workday if the group has no classes. In the case of a class in the morning is the meeting time 8.15-16.15.
A member of the group are allowed to leave at 14.00 if the group have no classes in the afternoon but have to work the remaining 2 hours and 15 minutes at home.
\section{Responsibility for own learning/mutual responsibility for learning}
Each group member has responsibility for his/her own learning at home and at class. But the group also has mutual responsibility for the groups learning while group work. 
Knowledge sharing is also important and the group uses SVN to share all work so it is available at all time to everyone in the group.